Memory-Efficient Mixed-Precision Implementations\\for Robust Explicit Model Predictive Control

### 2019-04-12 emsoft-2019/Cont_Syn.tex
fix

We implemented our algorithm in a Python script which interfaces between Matlab
and Daisy and which implements the high-level structure from~\autoref{lst:alg}.
The interface parses the output from Matlab and encodes the matrices \texttt{F,
G, H, K} and the error bounds in Daisy's input format.
\eva{Can we say something about parallelization?}

>>>>

We implemented our algorithm in a Python script which interfaces between Matlab
and Daisy and which implements the high-level structure from~\autoref{lst:alg}.
The interface parses the output from Matlab and encodes the matrices \texttt{F,
G, H, K} and the error bounds in Daisy's input format. The precision tuning for activation functions (line 12) and hyperplanes (line 13) can be efficiently done in parallel, because the analysis of a single region is completely independent from the others. Same holds for hyperplanes. 
A relatively simple improvement to the current parallelization could be to run precision tuning for hyperplanes and active functions together, without waiting for the latter to terminate. Nevertheless, we suspect a minimal impact on performance, because usually the number of hyperplanes is an order of magnitude greater than regions. Thus, this is the main bottleneck of the algorithm. 
%\eva{Can we say something about parallelization?}
